P2P-LLM: Collaborative LLM Inference

### 2025-05-05 docs/paper/main.tex
move figures

\subsection{Pareto Efficiency}

The optimal path is well defined when weights for nodes are clearly defined, but there is not an apparent way to define
weights for nodes in this case. In the P2P-LLM network, there are two competing criterion that define the weight of node: computational cost and price.
The algorithm described above uses a single objective (SO), while the optimal path in the network is a multi-objective (MO) optimization problem.
There are several way to find optimal solutions to MO optimization problems \citep{1599245}. The simplest way is to convert it to a SO optimization problem, and
since the shortest path algorithm is designed for SO objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
a weighed aggregate of the objectives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
The objective, or weight, of a node, $w_i$ is defined as.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
				width=10cm,
				height=6cm,
				xlabel={Computational Cost},
				ylabel={Price},
				xlabel style={font=\large},
				ylabel style={font=\large},
				xmin=0, xmax=10,
				ymin=0, ymax=10,
				xtick={0,2,4,6,8,10},
				ytick={0,2,4,6,8,10},
				grid=both,
				title={Pareto Frontier: Computational Cost vs. Price},
				legend pos=north east,
				legend style={font=\footnotesize}
			]

@@

		\end{axis}
	\end{tikzpicture}
	\caption{Pareto Frontier}
	\label{fig:Pareto-optimal}
\end{figure}

>>>>

\subsection{Pareto Efficiency}
\begin{figure}[h]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
				width=10cm,
				height=6cm,
				xlabel={Computational Cost},
				ylabel={Price},
				xlabel style={font=\large},
				ylabel style={font=\large},
				xmin=0, xmax=10,
				ymin=0, ymax=10,
				xtick={0,2,4,6,8,10},
				ytick={0,2,4,6,8,10},
				grid=both,
				title={Pareto Frontier: Computational Cost vs. Price},
				legend pos=north east,
				legend style={font=\footnotesize}
			]

@@

		\end{axis}
	\end{tikzpicture}
	\caption{Pareto Frontier}
	\label{fig:Pareto-optimal}
\end{figure}
The optimal path is well defined when weights for nodes are clearly defined, but there is not an apparent way to define
weights for nodes in this case. In the P2P-LLM network, there are two competing criterion that define the weight of node: computational cost and price.
The algorithm described above uses a single objective (SO), while the optimal path in the network is a multi-objective (MO) optimization problem.
There are several way to find optimal solutions to MO optimization problems \citep{1599245}. The simplest way is to convert it to a SO optimization problem, and
since the shortest path algorithm is designed for SO objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
a weighed aggregate of the objectives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
The objective, or weight, of a node, $w_i$ is defined as.
